Dynein project log

### 2017-01-14 thesis_stuff/thesis_stuff.tex
Add in new parameters from hunt

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & 6.8e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & 1.6e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & 1.9e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & 7.9e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & 4.6e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
  \end{tabular}
\end{center}

ARE THESE ANGLES RIGHT??????????????\\
